\hlc[green]{Uranyl Solvation by a Three-Dimensional Reference Interaction Site Model}

### 2015-06-17 doc/uo2_paper/uo2-II.tex
AM: there IS a vacany without the symmetry constraints

In QM calculations, we use symmetric models of uranyl aqua complexes
to compare PCM and RISM representations of the solvent in QM calculations.
The under-coordinated species does not feature a vacancy in the first
solvation shell \hlc[green]{without the symmetry constraint}. Instead, all water ligands are equivalent due to
symmetry, also for the five- and six-coordinated uranyl. These models
feature an additional intra-molecular degree of freedom, the uranyl
bond length, in contrast to the MM models discussed in the previous
section where the uranyl bond was fixed at a reasonable value.

>>>>

In QM calculations, we use symmetric models of uranyl aqua complexes
to compare PCM and RISM representations of the solvent in QM
calculations.  \hlc[cyan]{The symmetry constraints for the five- and
  six-coordinated uranyl are qualitatively consistent with the
  structures obtained by unconstrained optimization (see next
  section). However, the under-coordinated species does not feature a
  vacancy in the first solvation shell as in an unconstrained
  structure. Instead, all water ligands are evenly distributed in the
  equatorial plane.}  These models feature an additional
intra-molecular degree of freedom, the uranyl bond length, in contrast
to the MM models discussed in the previous section where the uranyl
bond was fixed at a reasonable value.
